An iterated Grothendieck construction of semi-cubical types

### 2022-02-23 paper/paper.tex
paper: polish a bit

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[!ht]\small
\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}

@@

@@

\begin{listing}[H]
  \begin{minted}[linenos]{coq}
    Theorem le_trans {p q n} : p <= q -> q <= n -> p <= n.
    (* ... a non-trivial proof ... *)
    Defined.
  \end{minted}
  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using an inductive approach}
\end{listing}

\begin{listing}[H]
  \begin{minted}[linenos]{coq}
    Definition le_trans {n m p} (Hnm : n <= m) (Hmp : m <= p) : n <= p :=
      fun q (Hqn : le' q n) => Hmp _ (Hnm _ Hqn).
  \end{minted}
  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using a nested implication}
\end{listing}

@@

\begin{listing}[H]
  \begin{minted}{coq}
    Record PartialBoxPrev (n : nat) (csp : Type@{l'}) := {
      box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
      (* [box' n D] is [box (n-1) D.1] *)
      box'' {p} (Hp : p.+2 <= n) : csp -> Type@{l} ;
      subbox' {p q} {Hp : p.+2 <= q.+2} (Hq : q.+2 <= n) (ε : side) {D : csp} :
        box' (↓ (Hp ↕ Hq)) D -> box'' (Hp ↕ Hq) D;
    }.

@@

@@

  \bibitem[Angiuli]{Angiuli17}
  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia),Robert Harper, \& Daniel R. Licata. arXiv preprint.

>>>>

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[H]\small
\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}

@@

\color{gray65}

@@

\begin{listing}[H]
  \begin{minted}{coq}
    Theorem le_trans {p q n} : p <= q -> q <= n -> p <= n.
    (* ... a non-trivial proof ... *)
    Defined.
  \end{minted}
  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using an inductive approach}
\end{listing}

\begin{listing}[H]
  \begin{minted}{coq}
    Definition le_trans {n m p} (Hnm : n <= m) (Hmp : m <= p) : n <= p :=
      fun q (Hqn : le' q n) => Hmp _ (Hnm _ Hqn).
  \end{minted}
  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using a nested implication}
\end{listing}

@@

\begin{listing}[H]
  \begin{minted}{coq}
    Record PartialBoxPrev (n : nat) (csp : Type@{l'}) := {
      box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
      box'' {p} (Hp : p.+2 <= n) : csp -> Type@{l} ;
      subbox' {p q} {Hp : p.+2 <= q.+2} (Hq : q.+2 <= n) (ε : side) {D : csp} :
        box' (↓ (Hp ↕ Hq)) D -> box'' (Hp ↕ Hq) D;
    }.

@@

\newpage

@@

  \bibitem[Angiuli]{Angiuli17}
  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. arXiv preprint.
